\documentclass[12pt]{article}
\oddsidemargin=0.0in
\evensidemargin=0.0in
\textwidth=6.5in
\topmargin=-0.35in
\textheight=9in
\usepackage[utf8]{inputenc}
\usepackage[russian]{babel}
%\usepackage{doublespace}
 
\begin{document}
\pagestyle{empty}
 
\begin{center}
{\LARGE {\bf Homework One}}\\
\bigskip
{\Large {\bf Thermodynamics}}\\
\bigskip
{\Large {\bf College of the Atlantic}}\\
\bigskip
{ {\bf Due Friday, January 10, 2025}}\\ 
\end{center}
\medskip


\noindent All problems are from the textbook, unless otherwise noted. 

\begin{enumerate}
\setlength{\itemsep}{-1mm}
  \item 1.4
%  \item 1.9
  \item 1.11
  \item 1.12
  \item 1.14
  \item This is a problem based on question 1.16 from the textbook.
    The goal is to use Newton's second law ($\vec{F}_{\rm net} =
    m\vec{a}$) and the ideal gas law to derive the barometric
    equation.  To do so, consider a slab of air with a thickness of
    $\Delta z$ at rest at a height $z$ above the surface of the earth.
    Denote by $M$ the mass of the air in the slab.  Let $A$ be the
    horizontal area of the slab.  
    \begin{enumerate}
    \item Use Newton's law to derive an expression for
      $\frac{dP}{dz}$, the rate at which pressure changes with
      altitude.  \emph{Hints:}
      \begin{itemize}
      \item The derivative is defined as:
        \begin{equation}
          \frac{dP}{dz} \, = \, \lim_{\Delta z \rightarrow 0}
          \frac{P(z+\Delta z) - P(z)}{\Delta z} \;.
        \end{equation}
      \item There are three forces acting on the slab.
      \end{itemize}
      \item Use your answer to the previous problem and the ideal gas
        law to show that:
        \begin{equation}
          \frac{dP}{dz} \, = \, -\frac{mg}{kT}P \;,
          \label{eq:barometric}
          \end{equation}
        where $m$ is the average mass of the air molecules.  This
        equation is known as the barometric equation.
      \item Show that, assuming that $T$ is constant, the solution to
        Eq.~(\ref{eq:barometric}) is given by:
        \begin{equation}
          P(z) \, = \, P(0) e^{-mgz/kT} \;,
          \label{eq:solution}
          \end{equation}
        where $P(0)$ is the pressure at sea level.
      \item Use Eq.~(\ref{eq:solution}) to calculate the pressure, in
        atmospheres, at the following locations:
        \begin{enumerate}
        \item Cadillac Mountain
        \item Katahdin Mountain
        \item The Zugspitze
        \item Nevado Huascar\'an
        %\item Cerro El Pital
        %\item Mount Elbrus
        %\item Гора Эльбрус
        \end{enumerate}
        Assume that the pressure at sea level is $1$ atm. 
    \end{enumerate}

\end{enumerate}






\end{document}
