\documentclass[12pt]{article}
\oddsidemargin=0.0in
\evensidemargin=0.0in
\textwidth=6.5in
\topmargin=-0.35in
\textheight=9in
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=magenta,
    filecolor=magenta,      
    urlcolor=blue,
    pdftitle={Calc III Homework 01},
    %pdfpagemode=FullScreen,
    }

\begin{document}
\pagestyle{empty}
 
\begin{center}
{\LARGE {\bf Homework Six}}\\
\bigskip
{\Large {\bf Calculus III}}\\
\bigskip
{\Large {\bf College of the Atlantic}}\\
\bigskip
{ {\bf Target Date: Friday, February 11, 2022}}\\  
\end{center}
\medskip


\noindent There are only WeBWorK problems this week.\\

\noindent {\bf Part 1: WeBWorK}.  Do Homework 06 which you will find 
on your \href{https://webwork.runestone.academy/webwork2/coa-feldman-es3028m-winter-2022/}{WeBWorK account}.\\
%I recommend doing the edfinity part of the
%homework first.  This will enable you to benefit edfinity's instant
%feedback before you do part two.\\

\end{document}

\noindent {\bf Part 2: Problems from the Textbook}.  Here are some
instructions for how to submit this part of the assignment.
\begin{itemize}
\item Do the problems by hand using pencil (or pen) and paper.
  There is no need to type of this assignment.
\item Make a pdf scan of your work using genius scan or some
  similar scanning app.  Please make the homework into a single
  pdf, not multiple pdfs.
\item Submit the assignment on google classroom.  Please don't
  email it to me.  (Between my two classes I will be receiving
  around 45 assignments a week.  Keeping track of them all in email 
  is challenging.)\\
\end{itemize}

\noindent {\bf Chapter 15.2}

\begin{enumerate}
\setlength{\itemsep}{-1mm}
\item 18
\end{enumerate}

\noindent {\bf Chapter 15.3}
\begin{enumerate}
\setlength{\itemsep}{-1mm}
\item 8
\item 29
\end{enumerate}

\noindent {\bf Project 5.2, page 823)}
\begin{enumerate}
\setlength{\itemsep}{-1mm}
\item 2a
\item 2b
\item 2c
\item Optional: 2d \& 2e
\end{enumerate}

\noindent {\bf Review Exercises, page 821}
\begin{enumerate}
\setlength{\itemsep}{-1mm}
\item Optional: 46 (I haven't tried this problem yet, but it looks
  potentially interesting and fun.
\end{enumerate}





\end{document}
