\documentclass[12pt]{article}
\oddsidemargin=0.0in
\evensidemargin=0.0in
\textwidth=6.5in
\topmargin=-0.35in
\textheight=9in
%\usepackage{doublespace}
 
\begin{document}
\pagestyle{empty}
 
\begin{center}
{\LARGE {\bf Homework One}}\\
\bigskip
{\Large {\bf Physics and Math of Sustainable Energy}}\\
\bigskip
{\Large {\bf College of the Atlantic}}\\
\bigskip
{ {\bf Due Friday, January 8, 2021}}\\ 
\end{center}
\medskip


\noindent There are two parts to this assignment.\\

\noindent {\bf Part 1: Edfinity}.  Do Homework 01 which you will find
on your edfinity account.  I recommend doing the edfinity part of the
homework first.  This will enable you to benefit edfinity's instant
feedback before you do part two.\\

\hspace{2mm}\\

\noindent {\bf Part 2: Problems from the Textbook}.  Here are some
instructions for how to submit this part of the assignment.
\begin{itemize}
\item Do the problems by hand using pencil (or pen) and paper.
  There is no need to type of this assignment.
\item Make a pdf scan of your work using genius scan or some
  similar scanning app.  Please make the homework into a single
  pdf, not multiple pdfs.
\item Submit the assignment on google classroom.  Please don't
  email it to me.  (Between my two classes I will be receiving
  over 40 assignments a week.  Keeping track of them all in email
  is challenging.)
\item Do problem 3.5 in pairs. Work with someone else in the class
  and hand in only one solution for the two of you.
\item If you want, you can do all the problems in pairs and hand
  in only one set of solutions.\\
\end{itemize}

\noindent The problems you should do are from {\bf Chapter 3} of the book: 

\begin{enumerate}
\setlength{\itemsep}{-1mm}
  \item 3.4
  \item 3.5\\
\end{enumerate}

\noindent Information about how to access the book will be sent out
via email and is also included on the pinned post on google
classroom. 






\end{document}
