\documentclass[12pt]{article}
\oddsidemargin=0.0in
\evensidemargin=0.0in
\textwidth=6.5in
%\topmargin=-.75in
%\textheight=9in
%\usepackage{doublespace}
 
\begin{document}
\pagestyle{empty}
 
\begin{center}
{\large {\bf Introduction to Computer Science}}\\
\medskip
{\large {\bf Homework Three}}\\
\medskip
{ {\bf Due Sunday January 23, 2011}}\\ 
\end{center}

\hspace{2mm}\\

\noindent General Instructions

\begin{itemize}
\setlength{\itemsep}{-1mm}
  \item Email me the program as a .py attachment.
  \item Name your programs with a helpful name.  Include your name
    somewhere in the file name.
  \item Your program should be fully commented.  Be sure to include
    your name and the date and an overall description of what the
    program does, in addition to any other comments that are needed. 
  \item My plan is to post these program on the website, since I
    thought it might fun to look at each other's creations.  If you
    don't want your program posted, just let me know. 
\end{itemize}


\begin{enumerate}

\item Write a program that makes use of the objects in the Zelle's
  graphics module to make an interesting picture.  Your program should
  make use of mutltiple objects: lines, points, polygons, rectangles,
  circles, text.  In addition, you might want to change the default
  size of the GraphWin.  

\item {\bf Optional:} Write a graphical user interface for a program
  that does currency conversion.  Follow the example for temperature
  conversion in Chapter 4.

\end{enumerate}


\end{document}
