\documentclass[12pt]{article}
\oddsidemargin=-0.20in
\evensidemargin=-0.20in
\textwidth=6.5in
\topmargin=-.28in
\textheight=9.2in
\usepackage{url}
 
\begin{document}
\pagestyle{empty}
 
\begin{center}
{\large {\bf Introduction to Computer Science}}\\
\medskip
{\large {\bf Homework Six}}\\
\medskip
{ {\bf Due Sunday February 20, 2011}}\\ 
\end{center}

%\hspace{2mm}\\

\noindent General Instructions

\begin{itemize}
\setlength{\itemsep}{-1mm}
  \item Please email me the programs as a .py attachment.
  \item Name your programs with a helpful name.  Include your name
    somewhere in the file name.
  \item Your program should be fully commented.  Be sure to include
    your name and the date and an overall description of what the
    program does, in addition to any other comments that are needed. \\
\end{itemize}



\noindent These exercises are intended to be mostly straightforward
practice of some of the conditional statements we've learned about
recently.  \\



\begin{enumerate}

  \item Write a program that calculates a grade point average.  Use a
    while loop so that the user can enter as many grades as he or she
    wants.  When done, the program tell the user the number of classes
    taken and the grade point average.  Only worry about letter
    grades, not +'s and -'s. 
\begin{enumerate}
    \item {\bf Optional.}  Enhance the program to account for + and -
      grades. 
    \item {\bf Optional:}  Add some code that catches errors in the
      user's entries.  E.g., if the user enters a number the program
      should print a warning.
\end{enumerate}  

  \item Write a function that takes as a parameter a list of numbers
    and returns the largest value in the list.  Write a program that
    tests this function.  The function should work for a list of
    arbitrary length.

  \item Problem 17 from page 232 of Zelle.

  \item Write a program that reads in a plain text file and calculates
    the average word length.  ({\bf Optional:}  Modify the program so
    it also calculates the value of the Automated Readability Index.
    See
    \url{http://en.wikipedia.org/wiki/Automated_Readability_Index}.) 

  \item {\bf Optional:}  Problem 14 in Zelle, page 264. 

  \item {\bf Optional:}  Problem 11--12 in Zelle, page 264. (A few
    years ago I wrote such a program for Suzanne Morse so she could
    calculate degree days for Maine for her Gardens and Greenhouses
    class.) 

  \item {\bf Optional:}  Write a program that takes a list as a
    parameter, and then sorts the list.  There are many different
    sorting algorithms.  Some are fast, some are slow.  For small
    lists it doesn't matter much.  Ponder this problem some on your
    own before you start googling or looking at wikipedia.  If someone
    handed you a deck of cards, what would be the quickest way to sort
    it?  

\end{enumerate}


\end{document}
