\documentclass[12pt]{article}
\oddsidemargin=0.0in
\evensidemargin=0.0in
\textwidth=6.5in
%\topmargin=-.75in
%\textheight=9in
%\usepackage{doublespace}
 
\begin{document}
\pagestyle{empty}
 
\begin{center}
{\large {\bf Introduction to Computer Science}}\\
\medskip
{\large {\bf Homework One}}\\
\medskip
{ {\bf Due 8:00pm  Sunday January 9, 2011}}\\ 
\end{center}

\hspace{2mm}\\

\noindent General Instructions:  For this assignment you will be
writing only one program.  Please do the following:

\begin{itemize}
\setlength{\itemsep}{-1mm}
  \item Email me the program as a .py attachment.
  \item Name your program file as follows:  {\tt <your first
    name>\_<age>.py}.  Use all lowercase letters.  For example, my
    program would be called: {\tt dave\_age.py}.
  \item Your program should be fully commented.  Be sure to include
    your name and the date and an overall description of what the
    program does, in addition to any other comments that are needed. 
\end{itemize}


\hspace{2mm}\\
\hspace{2mm}\\

\begin{enumerate}

\item Write a program that does the following:
\begin{enumerate}
\setlength{\itemsep}{-1mm}
  \item Prints a welcome message
  \item Asks the user for her or his name.
  \item Asks the user for her or his age.
  \item Prints a greeting to the user, using the user's correct name. 
  \item Prints the user's name, and also tells the user how old he or
    she will be in 2020.
  \item Prints a farewell message.

\end{enumerate}

Free free to improvise with this assignment a little if you want.  The
main goal here is to practice inputting text and numbers, printing
text and numbers, and doing simple arithmetic. 

\end{enumerate}






\end{document}
