\documentclass[12pt]{article}
\oddsidemargin=-0.20in
\evensidemargin=-0.20in
\textwidth=6.5in
\topmargin=-.28in
\textheight=9.2in
\usepackage{url}
 
\begin{document}
\pagestyle{empty}
 
\begin{center}
{\large {\bf Introduction to Computer Science}}\\
\medskip
{\large {\bf Homework Seven}}\\
\medskip
{ {\bf Due Sunday March 6, 2011}}\\ 
\end{center}

%\hspace{2mm}\\

\noindent General Instructions

\begin{itemize}
\setlength{\itemsep}{-1mm}
  \item Please email me the programs as a .py attachment.
  \item Name your programs with a helpful name.  Include your name
    somewhere in the file name.
  \item Your program should be fully commented.  Be sure to include
    your name and the date and an overall description of what the
    program does, in addition to any other comments that are needed. \\
\end{itemize}






\begin{enumerate}

  \item Modify the multiplying sheep program from class in the
    following ways: 
\begin{enumerate}
    \item Add a member variable {\tt age} to the Sheep class.
    \item Make it so that if the sheep reach a certain age (perhaps 10
      or so) they die
      and are removed from the program.
    \item {\bf Optional:}  Put in a delay so that the sheep don't
      start making new sheep until they reach a certain age. 
\end{enumerate}  

  \item {\bf Alternatively:} If you don't like the sheep example,
    write some other program involving classes.  The program should
    define one or more classes, and each class should have several
    member variables and methods.  One possibility is exercise 11 in
    chapter 10 from Zelle.

  \item Zelle, chapter 11, exercise 8. 

  \item  Zelle, chapter 11, exercise 10.

  \item {\bf Optional:}  Zelle, chatper 11, exercise 11.  I'd think
    one could have fun with this.  What would our website look like if
    the phrase human ecology was censored?  What would text look like
    if instead of censoring, words were changed or swapped in some
    way?  

\end{enumerate}


\end{document}
