
\documentstyle[12pt]{article}
\oddsidemargin=0in
\textwidth=6.2in
\topmargin=0in
\textheight=9.9in
%\usepackage{doublespace}

\renewcommand{\arraystretch}{1.3}

\begin{document}
\pagestyle{empty}

\begin{center}
{\Large {\bf Hydroelectric Power}} \\
\hspace{3cm}\\
\end{center}
\hspace{1cm}\\

Work in groups of two or three.  You should hand in only one write-up
per group.   Your reasoning should be clear, but I'm not looking for
elegant essays.  Be sure to cite any sources you consult, including web
sites.  This assignment will count as a 50 point homework.  Each
group member will receive the same grade/evaluation. 


\begin{enumerate}


\item The proposed Basin Mills Development on the Penobscot river
would have been a 64 foot high dam.  The average flow rate on the
Penobscot is 14,000 cubic feet per second.  What is the average amount
of power that this dam could deliver?  Assume that the falling water
can be converted into electric energy with an efficiency of 80\%.  

\item How much energy does a typical household use per month?  How
many households could this Dam supply power for?

\item  Do some research and find out how much power other plants
(hydro, nuclear, and fossil fuel) in Maine produce.

\item Estimate the flow rate of the small stream on campus.  In your
write up be sure to state how you performed this estimation.

\item Estimate how much power the little stream could provide.  To do
so you'll need to figure out the vertical drop of the stream.  Note
that building a dam wouldn't be required -- part of the stream could
be shunted into a long pipe.

\item  Translate the power of the little stream into some
understandable numbers.  Could the stream provide power for a dorm,
the entire campus, one office?  

\item How much per year would COA save on its electricity bill?

\end{enumerate}

Bonus Question/Other Stuff to Think About
\begin{itemize}
\item What are the ecological effects of divering small streams to
generate power?

\item How much power could be generated by tides?

\end{itemize}


\hspace{2mm}\\
The following web sites may prove useful:
\begin{itemize}

\item {\tt http://www.fortunecity.com/skyscraper/fortune/284/hydro.html}

\item {\tt http://zebu.uoregon.edu/1997/ph161/l29.html}

\item {\tt http://solstice.crest.org/renewables/re-kiosk/hydro/index.shtml}

\end{itemize}



\end{document}


