\documentclass[12pt]{article}
\oddsidemargin=0.0in
\evensidemargin=0.0in
\textwidth=6.5in
\topmargin=-0.35in
\textheight=9in
%\usepackage{doublespace}
 
\begin{document}
\pagestyle{empty}
 
\begin{center}
{\LARGE {\bf Homework Ten}}\\
\bigskip
{\Large {\bf Calculus I}}\\
\bigskip
{\Large {\bf College of the Atlantic}}\\
\bigskip
{ {\bf Due Friday, March 12, 2021}}\\ 
\end{center}
\medskip


\noindent There are two parts to this assignment.\\

\noindent {\bf Part 1: Edfinity}. There is no edfinity assignment this
week.\\   


\noindent {\bf Part 2: Problems from the Textbook}.  Here are some
instructions for how to submit this part of the assignment.
\begin{itemize}
\item Do the problems by hand using pencil (or pen) and paper.
  There is no need to type of this assignment.
\item Make a pdf scan of your work using genius scan or some
  similar scanning app.  Please make the homework into a single
  pdf, not multiple pdfs.
\item Submit the assignment on google classroom.  Please don't
  email it to me.  (Between my two classes I will be receiving
  over 40 assignments a week.  Keeping track of them all in email
  is challenging.)
%\item Do problem 40 in pairs. Work with someone else in the class
%  and hand in only one solution for the two of you.
\item If you want, you can do one or more of problems in pairs and hand 
  in only one set of solutions.\\
\end{itemize}


%\hspace{2mm}\\


\noindent {\bf Chapter 4.2:}
\begin{enumerate}
\setlength{\itemsep}{-1mm}
\item 35
\end{enumerate}

\noindent {\bf Chapter 4.4:}
\begin{enumerate}
\setlength{\itemsep}{-1mm}
\item 36
\item 45
\end{enumerate}

\noindent {\bf Chapter 4.5:}
\begin{enumerate}
\setlength{\itemsep}{-1mm}
\item 4
\item 6
\item 10
\end{enumerate}

\noindent {\bf Chapter 4, Project 3} (pages 253--4)\\

\noindent We'll work through this in class on Wednesday.  Do not do question
a.ii.   For part b, after taking the derivative and setting it equal
to zero, you may get an equation that is difficult to solve.  You can
use wolframalpha to solve it for you.








\end{document}
