\documentclass[12pt]{article}
\oddsidemargin=0.0in
\evensidemargin=0.0in
\textwidth=6.5in
\topmargin=-0.35in
\textheight=9in
%\usepackage{doublespace}
 
\begin{document}
\pagestyle{empty}
 
\begin{center}
{\LARGE {\bf Homework Eight}}\\
\bigskip
{\Large {\bf Calculus I}}\\
\bigskip
{\Large {\bf College of the Atlantic}}\\
\bigskip
{ {\bf Due Friday, February 26, 2021}}\\ 
\end{center}
\medskip


\noindent There are two parts to this assignment.\\

\noindent {\bf Part 1: Edfinity}.  Do Homework 08A, Homework 08B, and
Homework 08C, which you will find on your edfinity account.  I
recommend doing the edfinity part of the homework first.  This will
enable you to benefit edfinity's instant feedback before you do part
two.\\   


\noindent {\bf Part 2: Problems from the Textbook}.  Here are some
instructions for how to submit this part of the assignment.
\begin{itemize}
\item Do the problems by hand using pencil (or pen) and paper.
  There is no need to type of this assignment.
\item Make a pdf scan of your work using genius scan or some
  similar scanning app.  Please make the homework into a single
  pdf, not multiple pdfs.
\item Submit the assignment on google classroom.  Please don't
  email it to me.  (Between my two classes I will be receiving
  over 40 assignments a week.  Keeping track of them all in email
  is challenging.)
%\item Do problem 40 in pairs. Work with someone else in the class
%  and hand in only one solution for the two of you.
\item If you want, you can do one or more of problems in pairs and hand 
  in only one set of solutions.\\
\end{itemize}


%\hspace{2mm}\\


\noindent {\bf Chapter 3.4:}
\begin{enumerate}
\setlength{\itemsep}{-1mm}
\item 64
\end{enumerate}

\noindent {\bf Chapter 3.5:}
\begin{enumerate}
\setlength{\itemsep}{-1mm}
\item 40
\item 41
\end{enumerate}

\noindent {\bf Chapter 3.6:}\\

None.
%\begin{enumerate}
%\setlength{\itemsep}{-1mm}
%\item 43.  Show your work, and include a graph (either by hand or
%computer generated) of $f(x)$ illustrating where the concavity
%changes.  
%\end{enumerate}






\end{document}
