\documentclass[12pt]{article}
\oddsidemargin=0.0in
\evensidemargin=0.0in
\textwidth=6.5in
\topmargin=-0.35in
\textheight=9in
%\usepackage{doublespace}
\usepackage{hyperref}

\hypersetup{
    colorlinks=true,
    linkcolor=magenta,
    filecolor=magenta,      
    urlcolor=blue,
    %pdftitle={Overleaf Example},
    %pdfpagemode=FullScreen,
    }

\begin{document}
\pagestyle{empty}
 
\begin{center}
{\LARGE {\bf Homework Two}}\\
\bigskip
{\Large {\bf Chaos and Fractals}}\\
\bigskip
{\Large {\bf College of the Atlantic}}\\
\bigskip
{ {\bf Due Friday, September 22, 2023}}\\  
\end{center}
\medskip


\noindent There are two parts to this assignment.\\

\noindent {\bf Part 1: WeBWorK}.  Do Homework 01 which you will find
on your
\href{https://webwork-hosting.runestone.academy/webwork2/coa-feldman-es1026i-fall2023}{WeBWorK
  page}.  I recommend doing the WeBWorK part of the 
homework first.  This will enable you to benefit from WeBWorK's
instant, if not necessarily friendly, feedback before you do part two.\\

\noindent {\bf Part 2: Problems from the Textbook}.  Here are some
instructions for how to submit this part of the assignment.
\begin{itemize}
\item Do the problems by hand using pencil (or pen) and paper.
  There is no need to type of this assignment.
\item Make a pdf scan of your work using genius scan or some
  similar scanning app.  Please make the homework into a single
  pdf, not multiple pdfs.
\item Submit the assignment on google classroom.  Please don't
  email it to me.  (Between my two classes I will be receiving
  around 55 assignments a week.  Keeping track of them all in email
  is challenging.)
%\item Do problem 40 in pairs. Work with someone else in the class
%  and hand in only one solution for the two of you.
%\item If you want, you can do all the problems in pairs and hand
%  in only one set of solutions.\\
\end{itemize}

\noindent There are three textbook problems this week:

\begin{itemize}
\setlength{\itemsep}{-1mm}
\item Chapter 5, problem 5.2, on page 42. (Part (f) is optional. Do
  this if you want to exercise your algebra brain.)
\item Chapter 5, problem 5.6, on page 43.
\item Chapter 5, problem 5.7, on page 43. 
\end{itemize}






\end{document}
