
\documentclass[12pt]{article}
\oddsidemargin=0.0in
\evensidemargin=0.0in
\textwidth=6.5in
\topmargin=-.45in
\textheight=9in
%\usepackage{doublespace}
 
\begin{document}
\pagestyle{empty}
 
\begin{center}
{\Large {\bf Homework Eight}}\\
\smallskip
{\large {\bf Calculus III}}\\
\smallskip
{\large {\bf College of the Atlantic}}\\
\smallskip
{ {\bf Due Friday, February 26, 2016}}\\
\end{center}

\medskip
\noindent Please print out this cover sheet and attach it to your
problem solutions.  Completed assignments should go in my mailbox or
be handed in during class.  Please don't hand them to me other times,
as I might end up losing them and that would make us both sad. \\
\medskip

\noindent {\bf Your Name:} \underline{\hspace{5cm}}\\

\noindent {\bf Please list all the students you collaborated with on
  this assignment:}\\[10pt]
\underline{\hspace{7.1cm}} \hspace{2cm}
\underline{\hspace{7.1cm}}\\[10pt]
\underline{\hspace{7.1cm}} \hspace{2cm}
\underline{\hspace{7.1cm}}\\[10pt]
\underline{\hspace{7.1cm}} \hspace{2cm}
\underline{\hspace{7.1cm}}\\[10pt] 
%\bigskip

\noindent {\bf Did you get help from Corrie or Ian? }\\

\noindent {\bf Did you consult any resources other than our textbook
  or classnotes?  (If yes, please include citations in your
  solutions.)} \\

\noindent {\bf Were you able to get enough help so you could complete
  this assignment to your satisfaction?}\\

\noindent {\bf Approximately how many hours did you spend on this
  assignment?}\\ 

\noindent {\bf Anything else of note about this assignment?  (It was
  too hard, too easy, lots of fun, too repetitious...)}\\

\bigskip
\bigskip
\bigskip
\bigskip
\bigskip
\bigskip
\noindent The work I am turning in for this assignment is an accurate
reflection of my own understanding of the material.\\[14pt]

\noindent Signature: \underline{\hspace{7cm}} \hspace{1cm} Date:
\underline{\hspace{5cm}} 


\pagestyle{empty}
 
\begin{center}
{\large {\bf Calculus III}}\\
\medskip
{\large {\bf Homework Eight}}\\
\medskip
{ {\bf Due 16 February, 2016}}\\
\end{center}




\bigskip
\noindent {\bf Chapter 17.3:}
\begin{enumerate}
\setlength{\itemsep}{-1mm}
  \item 2
  \item 4
\end{enumerate}


%\noindent {\bf Chapter 18.1:}
%\begin{enumerate}
%\setlength{\itemsep}{-1mm}
%  \item 1--4
%  \item 7
%  \item 17--19
%\end{enumerate}

%\noindent {\bf Chapter 18.2:}
%\begin{enumerate}
%\setlength{\itemsep}{-1mm}
%  \item 3
%  \item 4
%  \item 5
%\end{enumerate}


\noindent {\bf Chapter 18.3:}
\begin{enumerate}
\setlength{\itemsep}{-1mm}
  \item 2
  \item 12
  \item 28
  \item 29
\end{enumerate}

\noindent {\bf Chapter 18.4:}
\begin{enumerate}
\setlength{\itemsep}{-1mm}
%  \item 3
%  \item 4
  \item 17
  \item 21--22 (Optional)
%  \item 22
\end{enumerate}

%\noindent {\bf Chapter 18 Projects (Optional)}
%\begin{itemize}
%  \item Both projects for chapter 18 explore different physics
%    applications of line integrals.  
%\end{itemize}

%\noindent {\bf Chapter 19.1:}
%\begin{enumerate}
%\setlength{\itemsep}{-1mm}
%  \item 2
%  \item 4
%  \item 8
%  \item 13
%  \item 30
%  \item 36 (Optional.  Recommended for physicists.)
%\end{enumerate}


\end{document}
