\documentclass[12pt]{article}
\oddsidemargin=0.0in
\evensidemargin=0.0in
\textwidth=6.5in
\topmargin=-.45in
\textheight=9in
%\usepackage{doublespace}
 
\begin{document}
\pagestyle{empty}
 
\begin{center}
{\Large {\bf Homework Four}}\\
\smallskip
{\large {\bf Calculus III}}\\
\smallskip
{\large {\bf College of the Atlantic}}\\
\smallskip
{ {\bf Due Friday, January 29, 2016}}\\
\end{center}

\medskip
\noindent Please print out this cover sheet and attach it to your
problem solutions.  Completed assignments should go in my mailbox or
be handed in during class.  Please don't hand them to me other times,
as I might end up losing them and that would make us both sad. \\
\medskip

\noindent {\bf Your Name:} \underline{\hspace{5cm}}\\

\noindent {\bf Please list all the students you collaborated with on
  this assignment:}\\[10pt]
\underline{\hspace{7.1cm}} \hspace{2cm}
\underline{\hspace{7.1cm}}\\[10pt]
\underline{\hspace{7.1cm}} \hspace{2cm}
\underline{\hspace{7.1cm}}\\[10pt]
\underline{\hspace{7.1cm}} \hspace{2cm}
\underline{\hspace{7.1cm}}\\[10pt] 
%\bigskip

\noindent {\bf Did you get help from Corrie or Ian? }\\

\noindent {\bf Did you consult any resources other than our textbook
  or classnotes?  (If yes, please include citations in your
  solutions.)} \\

\noindent {\bf Were you able to get enough help so you could complete
  this assignment to your satisfaction?}\\

\noindent {\bf Approximately how many hours did you spend on this
  assignment?}\\ 

\noindent {\bf Anything else of note about this assignment?  (It was
  too hard, too easy, lots of fun, too repetitious...)}\\

\bigskip
\bigskip
\bigskip
\bigskip
\bigskip
\bigskip
\noindent The work I am turning in for this assignment is an accurate
reflection of my own understanding of the material.\\[14pt]

\noindent Signature: \underline{\hspace{7cm}} \hspace{1cm} Date:
\underline{\hspace{5cm}} 


\hspace{2mm}\\
\newpage

 
\begin{center}
{\large {\bf Calculus III}}\\
\medskip
{\large {\bf Homework Four}}\\
\medskip
{ {\bf Due Friday January 22, 2016}}\\
\end{center}




\noindent {\bf Chapter 14.5:}   
\begin{enumerate}
\setlength{\itemsep}{-1mm}
  \item 12
  \item 36 Optional, recommended for physicists.
\end{enumerate}


\noindent {\bf Chapter 14.6:}
\begin{enumerate}
\setlength{\itemsep}{-1mm}
  \item 16
  \item 19
\end{enumerate}


\noindent {\bf Chapter 14.7:}
\begin{enumerate}
\setlength{\itemsep}{-1mm}
  \item 20--28, even only
  \item 37
\end{enumerate}

\noindent {\bf Chapter 15.1:}
\begin{enumerate}
\setlength{\itemsep}{-1mm}
  \item 2, 4.  To classify the critical points, just make a plot of
    the function. 
  \item 16
\end{enumerate}

\noindent {\bf Chapter 15.2:}
\begin{enumerate}
\setlength{\itemsep}{-1mm}
  \item 24
  \item 31 Optional, recomended for economists.
\end{enumerate}

\noindent {\bf Chapter 15 Projects:}
\begin{enumerate}
\setlength{\itemsep}{-1mm}
  \item Project 2, parts a--b
  \item Project 2, part c. Optional, but strongly recommended
  \item Project 2, parts d--e. Optional, recommended
\end{enumerate}




\end{document}
