\documentclass[12pt]{article}
\oddsidemargin=0in
\textwidth=6.25in
%\topmargin=-.75in
%\textheight=9in
\usepackage{epsf}

\renewcommand{\arraystretch}{1.3}

\begin{document}
\pagestyle{empty}

\begin{center}
{\large {\bf Lab 3: Momentum and Energy}}\\
\end{center}

\hspace{2mm}\\

\noindent {\bf Two-Dimensional Momentum Conservation}\\

\noindent Consider the multiflash photograph of a collision of two
billiard balls. Assume that the time interval between flashes is 0.1
seconds. Do the measurements below reasonably carefully. 

\begin{enumerate}
\setlength{\itemsep}{0mm}
   \item Choose a coordinate system. (A clever choice will make the
     problem a little easier.) 
   \item Determine the velocity vectors for each of the balls before
     and after the collision. Write the vector in component form. 
   \item Determine the momentum of the system before and after the
     collision. Write your answer in component form. 
   \item Is momentum conserved? \\
\end{enumerate}


\noindent {\bf Roller Coasters}
\begin{enumerate}
\setlength{\itemsep}{0mm}
   \item Take a look at the roller coaster apparatus. Answer the
   following questions before you start experimenting. Discuss as a
   group, and be sure to write down your hypotheses. 
\begin{enumerate}
\setlength{\itemsep}{-1mm}
   \item At the end of which track will the ball be moving the fastest? Why?
   \item If a race were held, the ball in which track would get to the
   bottom the first? Why?  
\end{enumerate}
   \item Now experiment and see if your hypotheses were correct. Discuss. \\
\end{enumerate}


\noindent {\bf More Estimation Practice}\\


\noindent Estimate the following quantities.  Aim to get results
accurate to within an order of magnitude (i.e., within roughly a power
of ten.)
\begin{enumerate}
  \setlength{\itemsep}{-1mm}
     \item How many trucks cross from Canada into Maine every year?
     \item How many piano tuners are there in the greater Boston area?  
      \item The total time, in years, that you have spent as a student
      in a classroom.  
\end{enumerate}
\end{document}

