\documentclass[12pt]{article}
\oddsidemargin=0.0in
\evensidemargin=0.0in
\textwidth=6.5in
\topmargin=-.45in
\textheight=9in
%\usepackage{doublespace}
 
\begin{document}
\pagestyle{empty}
 
\begin{center}
{\Large {\bf Homework Two}}\\
\smallskip
{\large {\bf Calculus III}}\\
\smallskip
{\large {\bf College of the Atlantic}}\\
\smallskip
{ {\bf Due Friday, September 22, 2017}}\\
\end{center}

\medskip
\noindent Please print out this cover sheet and attach it to your
problem solutions.  Completed assignments should go in my mailbox or
be handed in during class.  Please don't hand them to me other times,
as I might end up losing them and that would make us both sad. \\
\medskip

\noindent {\bf Your Name:} \underline{\hspace{5cm}}\\

\noindent {\bf Please list all the students you collaborated with on
  this assignment:}\\[10pt]
\underline{\hspace{7.1cm}} \hspace{2cm}
\underline{\hspace{7.1cm}}\\[10pt]
\underline{\hspace{7.1cm}} \hspace{2cm}
\underline{\hspace{7.1cm}}\\[10pt]
\underline{\hspace{7.1cm}} \hspace{2cm}
\underline{\hspace{7.1cm}}\\[10pt] 
%\bigskip

\noindent {\bf Did you get help from Alba or Vishal? }\\

\noindent {\bf Did you consult any resources other than our textbook
  or classnotes?  (If yes, please include citations in your
  solutions.)} \\

\noindent {\bf Were you able to get enough help so you could complete
  this assignment to your satisfaction?}\\

\noindent {\bf Approximately how many hours did you spend on this
  assignment?}\\ 

\noindent {\bf Anything else of note about this assignment?  (It was
  too hard, too easy, lots of fun, too repetitious...)}\\

\bigskip
\bigskip
\bigskip
\bigskip
\bigskip
\bigskip
\noindent The work I am turning in for this assignment is an accurate
reflection of my own understanding of the material.\\[14pt]

\noindent Signature: \underline{\hspace{7cm}} \hspace{1cm} Date:
\underline{\hspace{5cm}} 


\hspace{2mm}\\
\newpage



 
\begin{center}
{\large {\bf Calculus III}}\\
\medskip
{\large {\bf Homework Two}}\\
\medskip
{ {\bf Due Friday, September 22, 2017}}\\
\end{center}

\hspace{2mm}\\


%\noindent {\bf Chapter 13.1:}
%\begin{enumerate}
%\setlength{\itemsep}{-1mm}
%  \item 9--14
%  \item 15
%  \item 16
%  \item 22
%  \item 30
%   \item 32 Optional
%\end{enumerate}

\noindent {\bf Chapter 13.2:}
\begin{enumerate}
\setlength{\itemsep}{-1mm}
  \item 24
  \item 25
\end{enumerate}

\noindent {\bf Chapter 13.3:}
\begin{enumerate}
\setlength{\itemsep}{-1mm}
  \item 32
  \item 38
\end{enumerate}

\noindent {\bf Chapter 13, Project 2} (page 721).
\begin{enumerate}
\setlength{\itemsep}{-1mm}
  \item Part (a)
  \item Parts (b) and (c) are optional.  My recollection is that part
    (c) involives a bunch of algebra; you might need to turn to
    wolfram alpha.
\end{enumerate}

\noindent {\bf Chapter 14.1:}
\begin{enumerate}
\setlength{\itemsep}{-1mm}
  \item 2
  \item 6
  \item 8
  \item 22
\end{enumerate}


\end{document}
