\documentclass[12pt]{article}
\usepackage[margin=0.8in]{geometry}
%\oddsidemargin=0.0in
%\evensidemargin=0.0in
%\textwidth=6.5in
%\topmargin=-0.35in
\textheight=9in
\usepackage[colorlinks=true,
  urlcolor=blue
    ]{hyperref}
 
\begin{document}
\pagestyle{empty}
 
\begin{center}
{\LARGE {\bf Homework Two}}\\
\bigskip
{\Large {\bf Differential Equations}}\\
\bigskip
{\Large {\bf College of the Atlantic}}\\
\bigskip
{ {\bf Target Date: Friday, Jan 23, 2026}}\\ 
\end{center}
\medskip

Here are some instructions for how to submit the assignment.
\begin{itemize}
\item Do the problems by hand using pencil (or pen) and paper.
  There is no need to type this assignment.
\item If you've made a plot in google colab, you can just share the
  colab notebook with me. 
\item If you like working on a tablet, go for it. 
\item Make a pdf scan of your work using genius scan or some
  similar scanning app. Please make the homework into a single
  pdf, not multiple pdfs. And please please please not a png file. 
\item Submit the assignment on google classroom. Please don't
  email it to me. Thanks.\\
\end{itemize}

\noindent All problems are from the
\href{https://github.com/dpfeldman/Math-Modeling-with-Differential-Equations/blob/main/modeling.pdf}{textbook}. 

\begin{enumerate}
  \setlength{\itemsep}{1mm}
  \item Exercise 6.1 (We pretty much did this in class on Monday)
  \item Exercise 6.2 (We started this in class on Monday)
  \item Exercise 6.3
  \item \textbf{Optional} Exercise 6.4. Involves programming
  \item Short\footnote{One or two sentences is plenty!} reflections:
    \begin{enumerate}
      \item Did you work with any other humans on this assignment?
        (It's great if you did! Working with other humans is awesome.)
        If so, who, and how did you collaborate?
      \item GenAI: did you use it to help with this assignment? (It's
        ok if you did! GenAI is useful, sometimes, especially for
        programming. But it's important that what you turn in
        represents your understanding.) If so, how did you use it?
      \item Any other comments or reflections on this assignment?
        \end{enumerate}
\end{enumerate}

\noindent The optional problem 6.4 is strongly recommended for those
of you who took Intro to CS last term. This problem is a great way to
practice program design and syntax while deepening your understanding
of Euler's method. Give it a try.  

If you want, here is a
\href{https://colab.research.google.com/drive/1QmU56_DDXq-CEVSV5oHpAZcB2oF_AkYV?usp=sharing}{google
  colab notebook} that can use as a template for exercises 6.2 and
6.3. 



\end{document}
