\documentclass[12pt]{article}
\oddsidemargin=0.0in
\evensidemargin=0.0in
\textwidth=6.5in
\topmargin=-0.35in
\textheight=9in
\usepackage{hyperref}
 
\begin{document}
\pagestyle{empty}
 
\begin{center}
{\LARGE {\bf Homework Six}}\\
\bigskip
{\Large {\bf Physics and Math of Sustainable Energy}}\\
\bigskip
{\Large {\bf College of the Atlantic}}\\
\bigskip
{ {\bf Due Friday\footnote{Early next week is fine!}, October 24, 2025}}\\ 
\end{center}
\medskip


\noindent There are two parts to this assignment.\\

\noindent {\bf Part 1: WeBWorK}.  Do Homework 06 which you
will find the WeBWorK page here:
\url{https://webwork-hosting.runestone.academy/webwork2/coa-feldman-es1056i-fall2025}
I recommend doing the WeBWorK part of the homework first.  This will
enable you to benefit from WeBWorK's instant feedback before you do part
two.\\ 


\noindent {\bf Part 2: Problems from the Textbook}.  Here are some
instructions for how to submit this part of the assignment.
\begin{itemize}
\item Do the problems by hand using pencil (or pen) and paper.
  There is no need to type this assignment.
%\item If you like working on a tablet, go for it. 

\item Please scan your work and submit on google classroom.\\
  
%\item Make a pdf scan of your work using genius scan or some
%  similar scanning app.  Please make the homework into a single
%  pdf, not multiple pdfs.
%\item Submit the assignment on google classroom.  Please don't
%  email it to me.  (Between my two classes I will be receiving
%  around 60 assignments a week.  Keeping track of them all in email 
%  is challenging.)\\
\end{itemize}

\noindent The problems you should do are from {\bf Chapters
  19 and 26} of the book:  \\ 

\noindent {\bf Chapter 19}
\begin{enumerate}
\setlength{\itemsep}{-1mm}
\item 19.2
\item 19.3
\item 19.4 (Scientific notation is your friend! Please do not do this problem without it!!)
\item 19.5 \\
\end{enumerate}

\noindent {\bf Chapter 26}
\begin{enumerate}
  \setlength{\itemsep}{-1mm}
\item 26.3
\item 26.4
\item 26.6
\item 26.7
\end{enumerate}

\noindent {\bf Note: For Chapter 26 problems 3 and 4, you should not have to do difficult or
lengthy calculations. If you find yourself doing more than a line or two of math,
stop and ask for help!}\\

%\noindent Information about how to access the book is on the
%pinned post on google classroom. 


\end{document}
