\documentclass[12pt]{article}
\oddsidemargin=0.0in
\evensidemargin=0.0in
\textwidth=6.5in
\topmargin=-0.55in
\textheight=9in
%\usepackage{doublespace}
 
\begin{document}
\pagestyle{empty}
 
\begin{center}
{\LARGE {\bf Homework Six}}\\
\bigskip
{\Large {\bf Physics I}}\\
\bigskip
{\Large {\bf College of the Atlantic}}\\
\bigskip
{ {\bf Due Friday, October 29, 2021}}\\ 
\end{center}
\medskip

\noindent There are two parts to this assignment.\\

%\hspace{2mm}\\

\noindent {\bf Part 1: Edfinity}.  Do Homework 06 which you will find
on your edfinity account.  Note that there are three separate parts on
edfinity for Homework 06: one for Chapter C10, one for Chapter C11,
and one for Chapter C12.  I recommend doing the edfinity part of the
homework first.  This will enable you to benefit edfinity's instant
feedback before you do part two.\\ 


\noindent {\bf Part 2: Problems from the Textbook}.  Here are some
instructions for how to submit this part of the assignment.
\begin{itemize}
\item Do the problems by hand using pencil (or pen) and paper.
  There is no need to type of this assignment.
\item Make a pdf scan of your work using genius scan or some
  similar scanning app.  Please make the homework into a single
  pdf, not multiple pdfs.
\item Submit the assignment on google classroom.  Please don't
  email it to me.  (Between my two classes I will be receiving
  over 45 assignments a week.  Keeping track of them all in email
  is challenging.)\\
\end{itemize}

\noindent The textbook problems are:\\   

\noindent {\bf Chapter C10:}
%\setlength{\itemsep}{-1mm}
  \begin{enumerate}
  \item C10S.7\\
  \end{enumerate}

\noindent {\bf Chapter C11:}
  \begin{enumerate}
  \item C11S.5
  \item C11S.10\\
  \end{enumerate}
  
\noindent {\bf Chapter C12:}\\
There are no textbook problems for this chapter.  There are, however,
problems on Edfinity.







\end{document}
