\documentclass[12pt]{article}
\oddsidemargin=0.0in
\evensidemargin=0.0in
\textwidth=6.5in
\topmargin=-0.35in
\textheight=9in
%\usepackage{doublespace}
 
\begin{document}
\pagestyle{empty}
 
\begin{center}
{\LARGE {\bf Homework Four}}\\
\bigskip
{\Large {\bf Physics I}}\\
\bigskip
{\Large {\bf College of the Atlantic}}\\
\bigskip
{ {\bf Due Friday, October 8, 2021}}\\ 
\end{center}
\medskip

\noindent There are two parts to this assignment.\\

\hspace{2mm}\\

\noindent {\bf Part 1: Edfinity}.  Do Homework 03 which you will find
on your edfinity account.  Note that there are two separate parts on
edfinity for Homework 04: one for Chapter C06 and one for Chapter
C07.  I recommend doing the edfinity part of the homework first.  This
will enable you to benefit edfinity's instant feedback before you do
part two.\\ 


\noindent {\bf Part 2: Problems from the Textbook}.  Here are some
instructions for how to submit this part of the assignment.
\begin{itemize}
\item Do the problems by hand using pencil (or pen) and paper.
  There is no need to type of this assignment.
\item Make a pdf scan of your work using genius scan or some
  similar scanning app.  Please make the homework into a single
  pdf, not multiple pdfs.
\item Submit the assignment on google classroom.  Please don't
  email it to me.  (Between my two classes I will be receiving
  over 45 assignments a week.  Keeping track of them all in email
  is challenging.)\\
%\item Do problem 3.5 in pairs. Work with someone else in the class
%  and hand in only one solution for the two of you.
%\item If you want, you can do all the problems in pairs and hand
%  in only one set of solutions.\\
\end{itemize}

\noindent The textbook problems are:   

\begin{enumerate}
\setlength{\itemsep}{-1mm}
\item {\bf Chapter C6:}
  \begin{enumerate}
  \item C6S.4
  \item C6S.6
  \end{enumerate}

\item {\bf Chapter C7:}
  \begin{enumerate}
  \item C7S.1 (Note: This problem is not about springs.)
  \item C7R.2
  \end{enumerate}
\end{enumerate}







\end{document}
