
\documentclass[14pt]{extarticle}
\oddsidemargin=-0.250in
\evensidemargin=0.0in
\textwidth=6.75in
\topmargin=-.35in
\textheight=9in
\usepackage{epsf}
 

\begin{document}
\pagestyle{empty}

\begin{center}
{\Large {\bf Chapter C6: Intro to Energy Practice}}\\
\medskip
{\large {Physics I}}\\
\medskip
College of the Atlantic\\
\end{center}

\begin{enumerate}
\setlength{\itemsep}{5mm}

\item You drop a $5$ kg box of tempeh down a well that is $50$ meters
  deep.  What is the speed of the box right before it reaches the
  bottom of the well?  Do this problem two ways:
  \begin{enumerate}
    \item Use the ground as the reference point.
    \item Use a point ten meters above ground as the reference point.
\end{enumerate}


\item
  \begin{enumerate}
  \item A $0.25$ kg TAB mug is dropped the top of a $10$ meter
    platform.  What is its speed right before it hits the ground?
  \item What is the mug's speed if it is dropped from a $20$ platform?
  \item What is the speed just before impact of a $0.5$kg plate dropped from
    the $10$ meter platform? 
  \end{enumerate}

\item A TAB mug is thrown from a $10$ meter rooftop.  
  \begin{enumerate}
  \item When the mug hits the ground its speed is $20$ m/s.  At what
    speed was it thrown?
    \item Suppose the mug hits the ground at a speed of $10$ m/s?  In
      that case, at what speed was it thrown?
  \end{enumerate}

\item You throw a TAB mug straight up at 20 miles per hour.  How high
  in the air will it go?

\item How fast would you have to throw an object so that it reached
  the height of Cadillac mountain?
  
\item From what height should you drop something if you want it to hit
  the ground at $10$ m/s?  From what height should you drop something
  if you want it to hit the ground at $20$ m/s?

\end{enumerate}





\end{document}


