\documentclass[12pt]{article}
\oddsidemargin=0.0in
\evensidemargin=0.0in
\textwidth=6.5in
%\topmargin=-.75in
%\textheight=9in
\usepackage{amssymb}
\usepackage{ulem}
\usepackage{url}

\begin{document}
\pagestyle{empty}
 
\begin{center}
{\large {\bf Physics III}}\\
\medskip
{\large {\bf Homework Seven}}\\
\medskip
{ {\bf Due Friday 4 June, 2010}}\\
\end{center}

\hspace{2mm}\\


\begin{enumerate}
\setlength{\itemsep}{2mm}

\item Encrypt the following plaintext message {\tt THE BEARS ARE VERY
  SAD.}  For the key, use the description for course HS787, {\it
  Psychology and Social Factors for Carnivore Preservation}.   (The
  description can be found in the list of new courses, available at
  \url{http://www.coa.edu/assets/registrar/new_courses_fa10.pdf}.)

\item Decrypt the following message:  {\tt DFRKX TGJJH TJLZB HOIG}.
  The key is the description for course HS788 {\it Futures Studies}.  

\item A message was sent using the one-time pad shown below.  The
  coded message is {\tt QCZDICIJTBEXHNZZ}.  What is the decoded
  message?  Show at least some of your work to make it clear how
  you're decoding the message. 

{\large

\begin{center}
\begin{tabular}{ r r r r r r  }
9 & 2 & 4 & 25 & 8 & 22 \\
17 & 5 & 19 & 18 & 12 & 3 \\
22 & 1 & 21 & 8 & 11 & 20 \\
2 & 2 & 19 & 6 & 20 & 9 \\
0 & 5 & 21 & 7 & 13 & 10\\
\end{tabular}
\end{center}
}


\item Alice and Bob are using an EPR experiment to distribute a key
  for a cipher using the protocol we discussed in class and described
  in chapter 13 of Styer's book.  Alice
  observes:
\begin{equation}
  {\tt A1\,B1\,B0\,A0\,C0} \;\;\; {\tt B0\,A1\,B0\,B1\,C1} \;\;\; 
  {\tt A1\,A0\,C1\,C0\,B0} \;\;\; {\tt C1\,B1\,A0\,A0\,A1}
\end{equation}
While Bob observes:
\begin{equation}
  {\tt B0\,B0\,C0\,C1\,A1} \;\;\; {\tt B1\,C0\,B1\,B0\,A0} \;\;\; 
  {\tt C1\,B1\,C0\,B0\,C0} \;\;\; {\tt A1\,B0\,A1\,C0\,C0}
\end{equation}
What key would Alice and Bob end up using?  Was Eve listening in?  How
can you tell? 








\end{enumerate}


\end{document}
