\documentclass[12pt]{article}
\oddsidemargin=0.0in
\evensidemargin=0.0in
\textwidth=6.5in
\topmargin=-0.35in
\textheight=9in
\usepackage{hyperref}
 
\begin{document}
\pagestyle{empty}
 
\begin{center}
{\LARGE {\bf Homework Four}}\\
\bigskip
{\Large {\bf Physics and Math of Sustainable Energy}}\\
\bigskip
{\Large {\bf College of the Atlantic}}\\
\bigskip
{ {\bf Due Friday, October 11, 2024}}\\ 
\end{center}
\medskip


\noindent There are two parts to this assignment.\\

\noindent {\bf Part 1: WeBWorK}.  Do Homework 04 which you
will find the WeBWorK page here:
\url{https://webwork-hosting.runestone.academy/webwork2/coa-feldman-es1056-fall2024}.
I recommend doing the WeBWorK part of the homework first.  This will
enable you to benefit WeBWorK's instant feedback before you do part
two.\\ 


\noindent {\bf Part 2: Problems from the Textbook}.  Here are some
instructions for how to submit this part of the assignment.
\begin{itemize}
\item Do the problems by hand using pencil (or pen) and paper.
  There is no need to type this assignment.
\item If you like working on a tablet, go for it. 
\item Make a pdf scan of your work using genius scan or some
  similar scanning app.  Please make the homework into a single
  pdf, not multiple pdfs.
\item Submit the assignment on google classroom.  Please don't
  email it to me.  (Between my two classes I will be receiving
  around 60 assignments a week.  Keeping track of them all in email 
  is challenging.)\\
\end{itemize}



\noindent The problems you should do are from {\bf Chapters 18 and
  Appendix C} of the book:  \\

\noindent {\bf Chapter 18}
\begin{enumerate}
\setlength{\itemsep}{-1mm}
\item 18.11
\item 18.14
\item {\bf Optional}: 18-15--18.18. These problems lead you through a
  derivation of the Betz Limit. Recommended for folks who want a
  modest physics/math challenge. (Disrecommended for everyone
  else.)
%  \item And here's a Chapter 18 problem that's not in the book
%    yet... This problem is about the Bethel Windfarm, which is a few
%    kilometers to the West of Dimmitt, Texas, USA.
%    \begin{enumerate}
%      \item Find the wind farm on google or bing maps, and use the
%        mapping tool to estimate the area of the wind farm. I think
%        bing might be easier to use than google, since the picture is
%        a little clearer. Express your area in km$^2$.
%        \item What is the nameplate capacity of the Bethel Wind Farm?
%          To answer this, go to this website
%          \url{https://atlas.eia.gov/apps/all-energy-infrastructure-and-resources/explore},
%          which is a map of basically all US energy infrastructure.
%          Find the Bethel Wind Farm.  Click on the turbine icon, and
%          a pop-up window will appear with two pages of info. Click to
%          the second one, and you will see information about the
%          windfarm.
%      \item How much energy did the wind farm generate in 2022? On the
%        info tab on the previous website, you will see ``View Data in
%        the Electricity Data Browser'' on the top.  Click on the
%        link.  You will then be sent to a page that has information
%        about the electricity generated by the wind farm. 
%        Do not add up the monthly totals by hand. Click on the
%        ``annual'' tab and the website will do the addition for you.
%      \item What is the capacity factor of the Bethel Wind Farm?
%      \item What is the power density, in W/m$^2$, of the Bethel
%        Wind Farm? \\
%    \end{enumerate}
    \end{enumerate}


\noindent {\bf Appendix C}
\begin{enumerate}
  \setlength{\itemsep}{-1mm}
\item C.9
\item C.11\\ 
\end{enumerate}


\noindent Information about how to access the book will is on the
pinned post on google classroom. 


\end{document}
