\documentclass[12pt]{article}
\oddsidemargin=0.0in
\evensidemargin=0.0in
\textwidth=6.5in
\topmargin=-0.35in
\textheight=9in
\usepackage{hyperref}
 
\begin{document}
\pagestyle{empty}
 
\begin{center}
{\LARGE {\bf Homework Nine}}\\
\bigskip
{\Large {\bf Physics and Math of Sustainable Energy}}\\
\bigskip
{\Large {\bf College of the Atlantic}}\\
\bigskip
{ {\bf Due Friday, November 15, 2024}}\\ 
\end{center}
\medskip


\noindent There is only one part to this assignment.\\

\noindent {\bf Part 1: WeBWorK}.
Do Homework 09 which you will find the WeBWorK page here:
\url{https://webwork-hosting.runestone.academy/webwork2/coa-feldman-es1056-fall2024}
%I recommend doing the WeBWorK part of the homework first.  This will
%enable you to benefit WeBWorK's instant feedback before you do part
%two.\\ 


\noindent {\bf Part 2: Problems from the Textbook}.  Here are some
instructions for how to submit this part of the assignment.
\begin{itemize}
\item Do the problems by hand using pencil (or pen) and paper.
  There is no need to type this assignment.
\item If you like working on a tablet, go for it. 
\item Make a pdf scan of your work using genius scan or some
  similar scanning app.  Please make the homework into a single
  pdf, not multiple pdfs.
\item Submit the assignment on google classroom.  Please don't
  email it to me.  (Between my two classes I will be receiving
  around 60 assignments a week.  Keeping track of them all in email 
  is challenging.)\\
\end{itemize}



\noindent The problems you should do are from {\bf Chapters 10, 21, 14
  and 22} of the book:  \\  

\noindent {\bf Chapter 10}
\begin{enumerate}
  \setlength{\itemsep}{-1mm}
\item 10.5
\item 10.5 (Don't do any long calculations! This is supposed to be
  simple and quick!!) 
\item 10.7
\end{enumerate}

\noindent {\bf Chapter 21}
\begin{enumerate}
  \setlength{\itemsep}{-1mm}
\item 21.1
\end{enumerate}

\noindent {\bf Chapter 14}
\begin{enumerate}
  \setlength{\itemsep}{-1mm}
\item 14.2 (Optional, but recommended. Refutes a silly argument that
  is sometimes used to opposed wind power.)
\end{enumerate}

\noindent {\bf Chapter 22}
\begin{enumerate}
  \setlength{\itemsep}{-1mm}
\item 22.4
%\item 22.5
\item 22.6 (optional)\\
\end{enumerate}



\noindent Information about how to access the book is on the
pinned post on google classroom. 


\end{document}
