\documentclass[12pt]{article}
\oddsidemargin=0.0in
\evensidemargin=0.0in
\textwidth=6.5in
\topmargin=-0.55in
\textheight=9.5in
%\usepackage{doublespace}
 
\begin{document}
\pagestyle{empty}
 
\begin{center}
{\LARGE {\bf Homework Nine}}\\
\bigskip
{\Large {\bf Calculus II}}\\
\bigskip
{\Large {\bf College of the Atlantic}}\\
\bigskip
{ {\bf Due Friday, June 4, 2021}}\\ 
\end{center}
\medskip


\noindent There are two parts to this assignment.\\

\noindent {\bf Part 1: Edfinity}. There is no edfinity this week.
Sorry for the disappointment. 
%Do Homework 08A, and 08B, which you will find on your edfinity
%account.  %I recommend doing the  
%edfinity part of the homework first.  This will enable you to benefit
%edfinity's instant feedback before you do part two.\\

\noindent {\bf Part 2: Problems from the Textbook}.  Here are some
instructions for how to submit this part of the assignment.
\begin{itemize}
  \setlength{\itemsep}{0mm}
\item Do the problems by hand using pencil (or pen) and paper.
  There is no need to type of this assignment.
\item Make a pdf scan of your work using genius scan or some
  similar scanning app.  Please make the homework into a single
  pdf, not multiple pdfs.
\item Submit the assignment on google classroom.  Please don't
  email it to me.  (Between my two classes I will be receiving
  around 30 assignments a week.  Keeping track of them all in email
  is challenging.)
%\item Do problem 40 in pairs. Work with someone else in the class
%  and hand in only one solution for the two of you.
%\item If you want, you can do all the problems in pairs and hand
%  in only one set of solutions.\\
\end{itemize}

\noindent {\bf Chapter 9.3:}
\begin{enumerate}
  \setlength{\itemsep}{-1mm}
\item 13--19.  Just state if the series converges and give a
  one-sentence justification. 
\end{enumerate}

\noindent {\bf Chapter 9.4:}
\begin{enumerate}
  \setlength{\itemsep}{-1mm}
\item 4
\item 5
\item 18
\item 19
\item 64
\item 65
\end{enumerate}

\noindent {\bf Chapter 9.5:}
\begin{enumerate}
  \setlength{\itemsep}{-1mm}
\item 23
\item 24  
\end{enumerate}

\noindent {\bf Chapter 10.1:}
\begin{enumerate}
  \setlength{\itemsep}{-1mm}
\item 6
\end{enumerate}

\noindent {\bf Chapter 10.2:}
\begin{enumerate}
  \setlength{\itemsep}{-1mm}
\item 6
\item 7
\item 25
\item 26
\end{enumerate}

  
\end{document}
