 
\documentstyle[12pt]{article}
\oddsidemargin=0in
\textwidth=6.5in
\topmargin=0in
\textheight=9.9in
%\usepackage{doublespace}

\renewcommand{\arraystretch}{1.3}

\begin{document}
\pagestyle{empty}

\begin{center}
{\Large {\bf Flywheels}} \\
\hspace{3cm}\\
\end{center}
\hspace{1cm}\\

Work in groups of two or three.  You should hand in only one write-up
per group.   Your reasoning should be clear, but I'm not looking for
elegant essays.  Be sure to cite any sources you consult, including web
sites.  This assignment will count as a 50 point homework.  Each
group member will receive the same grade/evaluation. 


\begin{enumerate}

\item Read the Article, ``Reinventing the Wheel'' by Will Hively in
{\em Discover}, vol.~17, no.~8.  This article is on reserve in the
library and is also available online.  Go to
http://discover.com/
archive/index.html and search for articles written
by Hively.  

\item What is radius of the disks discussed in the fourth paragraph of
Hively's article?  (Calculate the radius using the revs per minute and
the speed on the edge of the disk given in the article.)


\item Calculate how much energy can be stored by this $50$ pound
disk.  State your answer in both Joules and kilowatt-hours.  

\item How much would it cost in Maine to spin up this flywheel?
Assume that electricity can be converted to flywheel energy at 96\%
efficiency.  

\item Estimate how far a car powered by 16 such flywheels could go
between recharges.  (Hint:  See problem C11R.2.)



\item Estimate how much energy is stored by the flywheels in use in
the pottery studio.  (If you have questions about their specification,
ask Ernie---he made them.)  Your write-up should state how you arrived
at this estimate.  


\end{enumerate}



Bonus Question/Other Stuff to Think About
\begin{itemize}
\item  Take a look at the technical report by Trinity Flywheel Power
on reserve in the library.  In the first equation, what are the
dimensions of $\sigma_k$ the {\em hoop stress}?  Do these units make
sense?  How do you think hoop stress is defined?

\item Find some more recent information on flywheels.  Has Bitterly
successfully tested his car?

\item What is preventing the widespread use of flywheel cars?  Is the
main barrier technological or economic?  

\end{itemize}

\hspace{2mm}\\
The following web sites may be of interest:
\begin{itemize}

\item {\tt http://www.trinityflywheel.com/index.htm  }

\item {\tt http://godzilla.lerc.nasa.gov/ppo/flywheel/program.html }

\item {\tt http://www.infp.fzk.de/wheel/english/wwwwheel.htm}

\item {\tt http://www.windbreak.com/ }

\item {\tt http://weirdrichard.com/FLYWHEELS.HTM}

\end{itemize}



\end{document}


