\documentclass[12pt]{article}
\oddsidemargin=0.0in
\evensidemargin=0.0in
\textwidth=6.5in
\topmargin=-0.35in
\textheight=9in
%\usepackage{doublespace}
 
\begin{document}
\pagestyle{empty}
 
\begin{center}
{\LARGE {\bf Homework Three}}\\
\bigskip
{\Large {\bf Physics and Math of Sustainable Energy}}\\
\bigskip
{\Large {\bf College of the Atlantic}}\\
\bigskip
{ {\bf Due Friday, October 1, 2021}}\\ 
\end{center}
\medskip


\noindent There are two parts to this assignment.\\

\noindent {\bf Part 1: Edfinity}.  Do Homework 03 which you will find
on your edfinity account.  I recommend doing the edfinity part of the
homework first.  This will enable you to benefit edfinity's instant
feedback before you do part two.\\


\noindent {\bf Part 2: Problems from the Textbook}.  Here are some
instructions for how to submit this part of the assignment.
\begin{itemize}
\item Do the problems by hand using pencil (or pen) and paper.
  There is no need to type of this assignment.
\item Make a pdf scan of your work using genius scan or some
  similar scanning app.  Please make the homework into a single
  pdf, not multiple pdfs.
\item Submit the assignment on google classroom.  Please don't
  email it to me.  (Between my two classes I will be receiving
  over 40 assignments a week.  Keeping track of them all in email
  is challenging.)\\
\end{itemize}


\noindent {\bf {\large IMPORTANT!!}}  Please be sure you have the most
current version of the textbook.  Go the webpage and do a hard
refresh!  Sorry for yelling.\\ 

\noindent {\bf From Chapter 1:}
\begin{enumerate}
\setlength{\itemsep}{-1mm}
\item 1.4 If you want to do this analysis for another country, go for
  it.  Just be sure to state which country you choose.  :)
\item 1.8\\
\end{enumerate}

\noindent {\bf From Chapter 15:}
\begin{enumerate}
\setlength{\itemsep}{-1mm}
\item 15.1
\item 15.2
\item 15.8\\
\end{enumerate}

\noindent Information about how to access the book was sent out
via email and is also included on the pinned post on google
classroom. 






\end{document}
