\documentclass[14pt]{extarticle}
\oddsidemargin=0.0in
\evensidemargin=0.0in
\textwidth=6.5in
\topmargin=-0.65in
\textheight=9in
\parindent=0in
%\usepackage{doublespace}
\usepackage{hyperref}

\hypersetup{
    colorlinks=true,
    linkcolor=magenta,
    filecolor=magenta,      
    urlcolor=blue,
    %pdftitle={Overleaf Example},
    %pdfpagemode=FullScreen,
    }

\begin{document}
\pagestyle{empty}
 
\begin{center}
{\LARGE {\bf Homework Five}}\\
\bigskip
{\Large {\bf Chaos and Fractals}}\\
\bigskip
{\Large {\bf College of the Atlantic}}\\
\bigskip
{ {\bf Due Friday, May 1, 2026\footnote{If you need more time,
      that's ok. Just let me know. Thanks!}}}\\  
\end{center}
\medskip


\noindent In what I hope is not too disappointing news, there is no
WeBWorK this week. So there is one and only one part to this
assignment.\\  

%\noindent {\bf Part 1: WeBWorK}.  Do Homework 04 which you will find
%on your
%\href{https://webwork-hosting.runestone.academy/webwork2/coa-feldman-es1026i-spring2026}{WeBWorK 
%  page}. \textbf{Note: Wait until after Tuesday's lab to do the WeBWorK!}\\ 
%I recommend doing the WeBWorK part of the 
%homework first.  This will enable you to benefit from WeBWorK's
%instant, if not necessarily friendly, feedback before you do part two.\\

%\hspace{2mm}\\

\noindent {\bf Part 1: Problems from the Textbook}.  Here are some
instructions for how to submit this part of the assignment.
\begin{itemize}
\item Do the problems by hand using pencil (or pen) and paper.
  There is no need to type of this assignment.
\item Make a pdf scan of your work using genius scan or some
  similar scanning app. Please make the homework into a single
  pdf, not multiple pdfs.
\item Submit the assignment on google classroom.  Please don't
  email it to me. 
%\item Do problem 40 in pairs. Work with someone else in the class
%  and hand in only one solution for the two of you.
%\item If you want, you can do all the problems in pairs and hand
%  in only one set of solutions.\\
\end{itemize}

\noindent Here are the textbook problems:

\begin{itemize}
  \setlength{\itemsep}{-1mm}
  \item Chapter 16, problem 5
  \item Chapter 16, problem 6
  \item Chapter 16, problem 9
  \item Chapter 16, problem 3
  \item Chapter 16, problem 7
  \item Chapter 16, problem 8. Optional!
    Fun. Challenging. Mindbending. If you do this problem, you may
    never be the same again.  
\end{itemize}

Yes, I know the problems are out of order. I did that on purpose. I
think doing them in the order I listed might be simpler. They're
sorta listed in order of increasing difficulty.

%You can find a scan of this problem
%\href{https://dpfeldman.github.io/Teaching/Chaos+Fractals.F23/pdf/page_14.pdf}{here}.  





\end{document}
