
\documentclass[12pt]{article}
\oddsidemargin=0in
\textwidth=6.25in
%\topmargin=-.75in
%\textheight=9in
%\usepackage{doublespace}

\renewcommand{\arraystretch}{1.3}

\begin{document}
\pagestyle{empty}

\begin{center}
{\large Class 1:  Some Warm-Up Group Exercises}\\
\end{center}

\begin{enumerate}

\item Introduce yourself to the other members of your group.\\

\item How many centimeters are in a meter?\\

\item How many square centimeters are in a square meter?\\

\item How many square centimeters are in 314 square meters?\\

\item Convert 65 miles per hour to meters per second.\\

%\item  Give an operational definition of area. \\

%\item  You make a small scale drawing of a garden you plan to plant.
%The area of your garden on the drawing is .25 ${\rm m}^2$.  For the
%actual garden, your drawing will get scaled up by a factor of $40$.
%What is the area of the real garden? \\

\item A tofu mishap occurs in the dining hall and a work-study student
is exposed to nasty soy chemicals which cause her to shrink by a
factor of $2$.  I.e., she's now half as tall, half as wide, etc.  
\begin{enumerate}
    \item By what factor has her volume decreased?  
    \item By what factor has her surface area decreased?
    \item By what factor has her mass decreased? \\
\end{enumerate}

\item What is the meaning or interpretation of the number $465/23$?\\

\item At A\&B Naturals $3$ pounds of lentils cost $5$ dollars. 
Answer the following questions using plain, everyday language.  Try not
use the word ``per''. 
\begin{enumerate}
\item What is the meaning or interpretation of the number $5/3$?
\item What is the meaning or interpretation of the number $3/5$? 
\item How much do $11$ pounds of lentils cost?
\item How many pounds of lentils can you get for $11$ dollars? 
\end{enumerate}

\end{enumerate}






\end{document}


