
\documentstyle[12pt,url,epsf]{article}
\oddsidemargin=0in
\textwidth=6.5in
%\topmargin=-.25in
%\textheight=9in
%\usepackage{doublespace}

\renewcommand{\arraystretch}{1.3}

\begin{document}

\pagestyle{empty}

\begin{center}
{\large {\bf First Presentation }}\\
\end{center}
\bigskip
\hspace{1cm}\\


{\bf Due Thursday September 26, 2002, In class} \\


Prepare a roughly twenty minute presentation on one of the following
topics: 
\begin{enumerate}
  \item Classical Potts Models
  \item Classical XY and Heisenberg Models
\end{enumerate}
You can decide amongst yourselves who does which topic.  In addition to
your presentation, it would also be helpful to prepare a {\em brief}\/
handout summarizing the key features of your models.

Your presentation should include most of the following information.


\begin{enumerate}

\item The critical exponents in two and three dimensions.  How and
when were these exponents calculate?  Are they exact?

\item The phase diagram in two and three dimensions.

\item What do the ordered phases look like?  What are the order
parameters? 

\item The upper critical dimension.

\item Experimental realizations of the model.

\item The universality class.  What other models and systems belong to
this universality class?

\item Other stuff that you found interesting.  For example, what more
exotic variations of the model have been studied -- e.g., external
fields, random interactions, random fields.  What has been found?


\end{enumerate}

\hspace{2mm}\\
We will evaluate your presentation roughly as follows.  Twenty-five
percent of the evaluation will be based on the organization and
preparation of the presentation, the remaining percent will be based
on your selection and explanation of your content.


\end{document}


